Lineal regression with one variable and one parameter for the cost function

### 2016-06-29 LinearRegression/Documentation/OneParam/OneParam.tex
adding joke to the oneParam document

\usepackage[utf8]{inputenc}
\usepackage{pgfplots}
\usepackage{caption}

@@

    for those of you who are not familiar with the derivarives, is highly
    recomendable to look at the Derivative fundamentals article that is in
    located in the documentation directory.\\

    Now lets analyze the formula, the fist simbol is the $\theta$ that is the
    parameter of the cost function, the second is the $:=$ which means assign,
    this make sence because we are trying to update the parameter of the
    function trying to make it as closer to the minimum as possible.

    \begin{figure}[ht!]
        \begin{tikzpicture}
            \begin{axis}[
                         title={Gradient decend with positive derivative},
                         xlabel=$\theta$,
                         ylabel=$J(\theta)$,
                         ymin=0, ymax=25,
                         xtick=\empty,
                         ytick=\empty
                        ]
                \addplot[mark=none, color=red]{x^2};

@@

                \addplot[color=blue, only marks]
                coordinates{
                    (4,16)
                    (3,9)
                    (2,4)
                    (1,1)
                    (0,0)
                };
            \end{axis}
        \end{tikzpicture}
    \end{figure}

    \begin{figure}[ht!]
        \begin{tikzpicture}
            \begin{axis}[
                         title={Gradient decend with negative derivative},
                         xlabel=$\theta$,
                         ylabel=$J(\theta)$,
                         ymin=0, ymax=25,
                         xtick=\empty,
                         ytick=\empty
                        ]
                \addplot[mark=none, color=red]{x^2};

@@

                \addplot[color=blue, only marks]
                coordinates{
                    (-4,16)
                    (-3,9)
                    (-2,4)
                    (-1,1)
                    (0,0)
                };
            \end{axis}
        \end{tikzpicture}
    \end{figure}

    \vspace{8cm}

>>>>

%

\usepackage[utf8]{inputenc}
\usepackage{pgfplots}
\usepackage{caption}
\usepackage{graphicx}
\graphicspath{ {Images/} }

@@

    for those of you who are not familiar with the derivatives, is highly
    recomendable to look at the Derivative fundamentals article that is in
    located in the documentation directory.\\

    Before explaining the deeper meaning of this derivative we are going to
    explain in other words what the gradient decend does, imagin that you are
    lost in a jungle that is kind of a valley, and you are trying to find your
    frinds that are in the lowest part of the valley, but you dont know exactly
    in what point of the valley are you, what do you do?\\

    %taken from http://bluepoppyholidays.com/wp-content/uploads/2014/10/Valley-of-flowers-from-top.jpg

    \vspace{2cm}

    \begin{figure}[h]
        \centering
        \includegraphics[scale=0.2]{Valley}
        \caption{What you are specting as a valley}
    \end{figure}

    \begin{figure}[h]
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                         title=What you have to imagin as a valley,
                         ymin=0, ymax=25,
                         xtick=\empty,
                         ytick=\empty
                        ]
                \addplot[mark=none, color=black]{x^2};

                \node[above] at (axis cs: 0,2) {Your};
                \node[above] at (axis cs: 0,0.5) {friends};

                \addplot[color=blue, only marks]
                    coordinates{
                        (0,0)
                    };

                \addplot[color=red, only marks]
                    coordinates{
                        (4,16)
                        (2,4)
                        (-3,9)
                    };

                \addplot[color=black, only marks]
                    coordinates{
                        (0,18)
                    };

                \node[above] at (axis cs: 0,18) {Your possible possition};

                \draw[thick, ->] (axis cs: 0,18) -- (axis cs: 3.7,16);
                \draw[thick, ->] (axis cs: 0,18) -- (axis cs: 1.8,4.4);
                \draw[thick, ->] (axis cs: 0,18) -- (axis cs: -2.9,9.3);
            \end{axis}
        \end{tikzpicture}
    \end{figure}

    What you shoul do

    Now lets analyze the formula, the fist simbol is the $\theta$ that is the
    parameter of the cost function, the second is the $:=$ which means assign,
    this make sence because we are trying to update the parameter of the
    function trying to make it as closer to the minimum as possible. Then we
    have a the actual value of $\theta$ followed by a substraction and a
    $\alpha$ simbol, we are goint to talk about this later, now we get to de
    most important part of the formula, the derivative ($\frac{d}{d \theta}$).\\

    the idea is that we are going to start in a point that is located at any
    part of the graphic, it could be far or close to the minimum, remember that
    this point is the result of the cost function for a line, and what we want
    to do is to start updating the value of $\theta$ because is the value that
    makes that the error will be big or small ($J(\theta)$).\\

    \begin{tikzpicture}
        \begin{axis}[
                     xlabel=$\theta$,
                     ylabel=$J(\theta)$,
                     ymin=0, ymax=25,
                     xtick=\empty,
                     ytick=\empty
                    ]
            \addplot[mark=none, color=red]{x^2};

            \draw[thick,->] (axis cs: 4,0) -- node[left]{$\theta_1$} (axis cs: 4,16);

            \addplot[color=blue, only marks]
            coordinates{
                (4,16)
                (2,4)
                (1,1)
                (0,0)
            };
        \end{axis}
    \end{tikzpicture}

    This can be done by calculating the direcction and that we want to follow

    \begin{tikzpicture}
        \begin{axis}[
                     title={Gradient decend with positive derivative},
                     xlabel=$\theta$,
                     ylabel=$J(\theta)$,
                     ymin=0, ymax=25,
                     xtick=\empty,
                     ytick=\empty
                    ]
            \addplot[mark=none, color=red]{x^2};

@@

            \addplot[color=blue, only marks]
            coordinates{
                (4,16)
                (3,9)
                (2,4)
                (1,1)
                (0,0)
            };
        \end{axis}
    \end{tikzpicture}

    \begin{tikzpicture}
        \begin{axis}[
                     title={Gradient decend with negative derivative},
                     xlabel=$\theta$,
                     ylabel=$J(\theta)$,
                     ymin=0, ymax=25,
                     xtick=\empty,
                     ytick=\empty
                    ]
            \addplot[mark=none, color=red]{x^2};

@@

            \addplot[color=blue, only marks]
            coordinates{
                (-4,16)
                (-3,9)
                (-2,4)
                (-1,1)
                (0,0)
            };
        \end{axis}
    \end{tikzpicture}
